### 2020-11-24 thesis/msc-thesis.tex
Changed formatting

\listoftodos

@@

\chapter{Context}
\todo[inline, caption={Expand Context Chapter}]{Add more content to this chapter}

Many enterprises provide digital tools which improve service usability for their customers. For example: If somebody wants to watch a movie, he does 
not drive to the nearest store to buy a DVD but instead uses websites providing video on demand (VoD). The reason is: 
VoD enterprises provide tools for digital customer self-service (DCSS). A customer can easily access the video over a website on his own.
DCSS becomes increasingly relevant, as the german government introduced requirements for DCSS in many recent regulations. 
Most prominent are  "Onlinezugangsgesetz" (OZG), "Datenschutzgrundverordnung" (DSGVO) and "Digitale Versorgung Gesetz" (DVG).

@@

\todo[inline, caption={Expand Objectives Chapter}]{Add more content to this chapter}

@@

\todo[inline, caption={Write Structure of Work Chapter}]{Briefly explain each chapter and their relationships}

@@

As tody most large enterprises provide DCSS, it can be assumed, that at a given size of an enterprise (measured in number of customers), the benefits of DCSS
surpass its disadvantages.

@@

\todo[inline, caption={Research Governmental Regulations Chapter}]{Explain the three regulations in general, what their purpose is what their challenges are}

@@

\todo[inline, caption={Write DCSS Providers Chapter}]{Explain what DCSS Providers are (what services they can provide) and how they can help creating DCSS.
     Also explain the concept of a business connector as technological communication point of the DCSS provider}

@@

\todo[inline, caption={Write Enterprise Architectures Chapter}]{Introduce Enterprise Architectures and challenges such as heterogeneous systems when trying to model them}

@@

\todo[inline, caption={Write Integration Chapter}]{Introduce the concept of integration. What are challenges in general and what would be an ideal integration.
     Also explain the approach towards integration used (messaging, patterns)}

@@

\todo[inline, caption={Research DCSS Scenarios Chapter}]{
     \begin{enumerate}
          \item Should governmental regulations be the focus of scenarios? => good resources for OZG
     \end{enumerate}
}

@@

\todo[inline, caption={Research Relevant Systems and Data Chapter}]{Explain the approach of modeling enterprise architectures by EAPs and explain the used EAPs.
     Analyze which system and data bricks of the system architecture could be necessarry for DCSS}

@@

\todo[inline, caption={Research Business Connector Chapter}]{Construct the model of the business connector}

@@

\todo[inline, caption={Integration Architecture Chapter}]{Create the integration architecture}

>>>>

@@

\chapter{Context}

Many enterprises provide digital tools which improve service usability for their customers. For example: If somebody wants to watch a movie, he does not drive to the nearest store to buy a DVD but instead uses websites providing video on demand (VoD). The reason is: VoD enterprises provide tools for digital customer self-service (DCSS). A customer can easily access the video over a website on his own. DCSS becomes increasingly relevant, as the German government introduced requirements for DCSS in many recent regulations. Most prominent are  "Onlinezugangsgesetz" (OZG), "Datenschutzgrundverordnung" (DSGVO) and "Digitale Versorgung Gesetz" (DVG).

@@

@@

@@

As today most large enterprises provide DCSS, it can be assumed, that at a given size of an enterprise (measured in number of customers), the benefits of DCSS surpass its disadvantages.

@@

@@

@@

@@

@@

@@

@@

@@
